Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-25 cordillera-cycle.tex
Rescale param table to fit new copernicus layout.
Last small changes before sending to co-authors.

      The simulations presented here were run using the Parallel Ice Sheet
      Model (PISM, development version~8ff7cbe), an open source, finite
      difference, shallow ice sheet model \citep{PISM-authors.2015}. The
      model requires input on basal topography, sea level, geothermal heat
      flux and climate forcing. It computes the evolution of ice extent and
      thickness over time, the thermal and dynamic states of the ice sheet,
      and the associated lithospheric response.

@@

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      PhD defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. We thank Shawn Marshall, Alexander Jarosch and Andrew Stumpf for
      their constructive and complementary reviews on the first manuscript.
      This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC) and by the Swiss National
      Supercomputing Centre (CSCS) allocation no.~s573 to J.~Seguinot.
\end{acknowledgements}

@@

\begin{table*}
\caption{%
      Default parameter values used in the ice sheet model.}
\label{tab:params}
\scalebox{.85}[.85]
{\begin{tabular}{llrll}
    \tophline
    Not.    & Name & Value & Unit & Source \\
    \middlehline
    \multicolumn{2}{l}{{Ice rheology}} \\
    \cline{1-5}

>>>>

      The simulations presented here were run using the Parallel Ice Sheet
      Model (PISM, version~0.7.2), an open source, finite
      difference, shallow ice sheet model \citep{PISM-authors.2015}. The
      model requires input on basal topography, sea level, geothermal heat
      flux and climate forcing. It computes the evolution of ice extent and
      thickness over time, the thermal and dynamic states of the ice sheet,
      and the associated lithospheric response.

@@

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      PhD defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. We thank Shawn Marshall, Alexander Jarosch and Andrew Stumpf for
      their constructive and complementary reviews.
      This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC) and by the Swiss National
      Supercomputing Centre (CSCS) allocation no.~s573 to J.~Seguinot.
\end{acknowledgements}

@@

\begin{table*}
\caption{%
      Default parameter values used in the ice sheet model.}
\label{tab:params}
\scalebox{.75}[.75]
{\begin{tabular}{llrll}
    \tophline
    Not.    & Name & Value & Unit & Source \\
    \middlehline
    \multicolumn{2}{l}{{Ice rheology}} \\
    \cline{1-5}
